\Large{Research Seminar Software Science} \\ \huge{Simulation of monadic effects in Haskell}

### 2018-06-16 paper.tex
finished variable assignment section

    \begin{tcolorbox}
    \begin{lstlisting}[language=Haskell] 
    is_operator :: Parse Operator 
    is_operator = is_arith_op +++ is_comp_op
    \end{lstlisting}
    \end{tcolorbox}
    \subsubsection{While Loop}

>>>>

    \begin{tcolorbox}
    \begin{lstlisting}[language=Haskell] 
    is_operator :: Parse Operator 
    is_operator = is_arith_op +++ is_comp_op
    \end{lstlisting}
    \end{tcolorbox}

    \noindent The creation of the \textbf{is\textunderscore operator} parser makes it viable to finally build the variable assignment parser where the right side contains an operator between two variable names.

    \begin{tcolorbox}
    \begin{lstlisting}[language=Haskell] 
    parse_assignment_op :: Parse AST
    parse_assignment_op  = isword `bind` \leftvar -> tokenize " := " 
                                  `bind` \eq -> isword 
                                  `bind` \leftopvar -> singleChar ' ' 
                                  `bind` \space2 -> is_operator 
                                  `bind` \operator -> singleChar ' ' 
                                  `bind` \space3 -> isword 
                                  `bind` \rightopvar -> 
        result (AssignmentOp leftvar leftopvar operator rightopvar)
    \end{lstlisting}
    \end{tcolorbox}

    \noindent Several \textbf{bind} operators have been used to construct this parser showing how the concept of monadic \textit{sequencing} keeps the steps transparent and provides a smooth transition between the different parsers used.  
    \subsubsection{While Loop}
